Manuscript Code

### 2022-10-06 Manuscript Code.Rmd
Update Manuscript Code.Rmd
Redlining_blocks_long needs the unique to be defined first, so switching these 2 code blocks

``` {r}

@@

redlining_blocks_unique %>%
  group_by(income_group) %>%
  summarise(pop = sum(bk_tot_pop_2010),
            ufp = weighted.mean(pnc_noscreen, bk_tot_pop_2010),
            ufp_pct_diff = per_diff(ufp, 7192),
            bc = weighted.mean(ma200_ir_bc1, bk_tot_pop_2010),
            bc_pct_diff = per_diff(bc, 557),
            no2 = weighted.mean(no2, bk_tot_pop_2010),
            no2_pct_diff = per_diff(no2, 9.76),
            pm2.5 = weighted.mean(pm2.5_ug_m3, bk_tot_pop_2010),
            pm2.5_pct_diff = per_diff(pm2.5, 4.92))

>>>>

``` {r}
redlining_blocks_unique %>%
  group_by(income_group) %>%
  summarise(pop = sum(bk_tot_pop_2010),
            ufp = weighted.mean(pnc_noscreen, bk_tot_pop_2010),
            ufp_pct_diff = per_diff(ufp, 7192),
            bc = weighted.mean(ma200_ir_bc1, bk_tot_pop_2010),
            bc_pct_diff = per_diff(bc, 557),
            no2 = weighted.mean(no2, bk_tot_pop_2010),
            no2_pct_diff = per_diff(no2, 9.76),
            pm2.5 = weighted.mean(pm2.5_ug_m3, bk_tot_pop_2010),
            pm2.5_pct_diff = per_diff(pm2.5, 4.92))

@@
